DATA 621 - Business Analytics and Data Mining

### 2020-11-26 HW5/HW5-Draft.Rmd
1) Move data.table after dplyr to minimize conflicts between packages 2) Copyediting 3) Move Yeo-Johnson citation to REFERENCES

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(data.table)
library(mice)
library(pscl)
library(mpath)
library(dplyr)

@@

```{r graphsD, fig.height=5, fig.width=7}
# Using epanechnikov kernel to generate kernel-smoothed densities
ggplot(predictorDTM[!is.na(metric) & metric %chin% nmtrnDUB], aes(x = value)) +
  geom_density(kernel = 'epanechnikov') +
  facet_wrap( ~ metric, scales = 'free') +
  ggtitle('Kernel-smoothed Density of Numeric Predictors')
```

@@

## Poisson Model #2 & Multiple Linear Regrssion Model #1

The right balance of the chemical properties of the wine is essential to make 
it tastes, looks, and smells delightful, in addition to having a long shelf-life.
Typically, citric acid and alcohol are the main positive attributes a wine 
should have, while volatile acidity and sulphates are the main negative ones. 
However, the dataset has negative values instead of near-zero in some of these 
variables describing the chemical properties of the wine. Because little is given 
about whether or not these variables were normalized, absolute values will be 
taken assuming there was an error made during data collection.

Lastly, to handle missing data for `STARS`, they will be replaced by 0, while 
the chemical properties will be imputed. Because the predictive mean matching 
imputation method combines the standard linear regression and the nearest-neighbor 
imputation approach, Model Set #2 elected to fill in missing values of a 
continuous variable by using it. Afterward, the data is pre-processed to fulfill 
the assumption of normality using the Yeo-Johnson transformation 
[(Yeo & Johnson, 2000)](https://www.jstor.org/stable/2673623?seq=1). This technique 
attempts to find the value of lambda that minimizes the Kullback-Leibler distance 
between the normal distribution and the transformed distribution. This method 
has the advantage of working without having to worry about the domain of x.

@@

  * Kuhn, M. (2019, March 27). *The `caret` Package*.
  https://topepo.github.io/caret/pre-processing.html#imputation

>>>>

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(mice)
library(pscl)
library(mpath)
library(dplyr)
library(data.table)

@@

```{r graphsD, fig.height=5, fig.width=7}
# Using Epanechnikov kernel to generate kernel-smoothed densities
ggplot(predictorDTM[!is.na(metric) & metric %chin% nmtrnDUB], aes(x = value)) +
  geom_density(kernel = 'epanechnikov') +
  facet_wrap( ~ metric, scales = 'free') +
  ggtitle('Kernel-smoothed Density of Numeric Predictors')
```

@@

## Poisson Model #2 & Multiple Linear Regression Model #1

The right balance of the chemical properties of the wine is essential to make it
taste, look, and smell delightful, in addition to having a long shelf-life.
Typically, citric acid and alcohol are the main positive attributes a wine
should have, while volatile acidity and sulphates are the main negative ones. 
However, the dataset has negative values instead of near-zero in some of these 
variables describing the chemical properties of the wine. Because little
information is given whether or not these variables were normalized, absolute
values will be taken assuming there was an error made during data collection.

Lastly, to handle missing data for `STARS`, they will be replaced by 0, while 
the chemical properties will be imputed. Because the predictive mean matching 
imputation method combines the standard linear regression and the
nearest-neighbor imputation approach, Model Set #2 elected to fill in the
missing values of a continuous variable by using mean-matching imputation.
Afterward, the data is pre-processed to fulfill the assumption of normality
using the Yeo-Johnson transformation (2000). This technique attempts to find the
value of lambda that minimizes the Kullback-Leibler distance between the normal
distribution and the transformed distribution. This method has the advantage of
working without having to worry about the domain of x.

@@

  * Kuhn, M. (2019, March 27). *The `caret` Package*.
  https://topepo.github.io/caret/pre-processing.html#imputation
  * Yeo, I., & Johnson, R. (2000). A New Family of Power Transformations to
  Improve Normality or Symmetry. **Biometrika**, 87(4), 954--959.
  Retrieved November 26, 2020, from http://www.jstor.org/stable/2673623
